Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-06 popl24/minicat.tex
checkpoint

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide the random tape and secret inputs to protocols, and record
view assignments. Memories $\store$ are finite (partial) mapping from
variables to binary values $\beta \in \{0,1\}$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto \beta\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = \beta$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store_1 \subseteq \store_2$ iff
$\dom(\store_1) \subseteq \dom(\store_2)$ and $\store_1(x) =
\store_2(x)$ for all $x \in \dom(\store_1)$. We write $\store_1 \cap
\store_2$ to denote the combination of $\store_1$ and $\store_2$
assuming $\store_1(x) = \store_2(x)$ for all $x \in \dom(\store_1)
\cap \dom(\store_2)$, otherwise $\store_1 \cap \store_2$ is undefined.

@@

\begin{example}[Oblivious Transfer]
  \label{example-OT}
  In \cite{barthe2019probabilistic} a protocol for $\ttt{OT}$ is defined that we recreate as
  follows, where client 2 is the receiver and client 1 is the sender. Whereas
  in \cite{barthe2019probabilistic} a trusted third party provides the sender and receiver with
  shared randomness, in our version both clients refer to the oracle $\ttt{H}$
  to obtain shared random values. 
\begin{verbatimtab}
  v[2, rd] := select(flip[2, d], H[r1], H[r0]);
  v[1, e] := s[2, c] xor flip[2, d];
  v[2, f0] := s[1, m0] xor select(v[1, e], H[r1], H[r0]);
  v[2, f1] := s[1, m1] xor select(not v[1, e], H[r1], H[r0]);
  v[2, mc] := select(s[2, c], v[2, f1], v[2, f0]) xor v[2, rd]
\end{verbatimtab}
Below we will discuss how to automatically verify security properties
of this protocol that correspond to the properties proven manually in
\cite{barthe2019probabilistic}, and additionally how to automatically verify its passive
security in the simulator model. With respect to our language primitives,
we note that this protocol is probabilistically equivalent to the
following:
\begin{verbatimtab}  
  v[2, mc] := OT(s[2, c], s[1, m1], s[1, m0])
\end{verbatimtab}
\end{example}

>>>>

\emph{Memories} are fundamental to the semantics of $\fedcat$ and
provide the random tape and secret inputs to protocols, and record
view assignments. Memories $\store$ are finite (partial) mapping from
variables to binary values $\beta \in \{0,1\}$. The \emph{domain} of a
memory is written $\dom(\store)$ and is the finite set of variables on
which the memory is defined. We write $\store\{ x \mapsto \beta\}$ for
$x\not\in\dom(\store)$ to denote the memory $\store'$ such that
$\store'(x) = \beta$ and otherwise $\store'(y) = \store(y)$ for all $y
\in \dom(\store)$. We write $\store_1 \subseteq \store_2$ iff
$\dom(\store_1) \subseteq \dom(\store_2)$ and $\store_1(x) =
\store_2(x)$ for all $x \in \dom(\store_1)$. We write $\store_1 \cap
\store_2$ to denote the combination of $\store_1$ and $\store_2$
assuming $\store_1(x) = \store_2(x)$ for all $x \in \dom(\store_1)
\cap \dom(\store_2)$, otherwise $\store_1 \cap \store_2$ is undefined.
We write $\store_1 \subseteq \store_2$ iff $\store_1 \cap \store_2
= \store_1$.

@@

\begin{example}[Oblivious Transfer]
  \label{example-OT}
  In \cite{barthe2019probabilistic} a protocol for $\ttt{OT}$ is
  defined that we recreate as follows, where client 2 is the receiver
  and client 1 is the sender, and a trusted third party provides the
  sender and receiver with shared randomness. The secret \ttt{s[2,c]}
  is the receiver's choice bit, and \ttt{s[1,m0]} and \ttt{s[1,m1]}
  are the sender's two message options that the receiver chooses from. 
\begin{verbatimtab}
  v[1,r0] := s[3,r0];
  v[1,r1] := s[3,r1];
  v[2,d] := flip[3,d];
  v[2,rd] := select(flip[3,d], s[3,r1], s[3,r0]);
  v[1,e] := s[2,c] xor v[2,d];
  v[2,f0] := s[1,m0] xor select(v[1, e],v[1,r1],v[1,r0]);
  v[2,f1] := s[1,m1] xor select(not v[1, e],v[1,r1],v[1,r0]);
  v[2,mc] := select(s[2,c],v[2,f1],v[2,f0]] xor v[2,rd)
\end{verbatimtab}
Below we will discuss how to automatically verify security properties
of this protocol that correspond to the properties proven manually in
\cite{barthe2019probabilistic}, and additionally how to automatically
verify its passive security in the simulator model. With respect to
our language primitives, we note that this protocol is equivalent to
the following:
\begin{verbatimtab}  
  v[2,mc] := OT(s[2,c], s[1,m1], s[1,m0])
\end{verbatimtab}
\end{example}
